% \part{Conclusion and Future Work}

\section{Conclusion}
This thesis has successfully explored the development of a naked-eye 3D system, utilizing monocular distance measurement and off-axis perspective projection to create a viable three-dimensional viewing experience without the necessity for specialized eyewear and depth measurement devices. 

Significant technical achievements of this project encompass the implementation of monocular head-traking and image correction algorithms, which have been designed to ensure real-time 3d effects low-cost and accuracy. The integration of monocular ranging techniques with off-axis projection has been pivotal in lowcost 3D effect, providing a more flexible and accessible alternative to traditional depth-camera-based methods. The proposed head-tracking system, which leverages facial keypoint detection and the ePnP algorithm, has been instrumental in enabling effective monocular head tracking, while the novel image correction algorithm has optimized image display on curved screens, enhancing the realism of the 3D experience.

\section{Future Work}
Monocular head-tracking and off-axis projection have been instrumental in the development of a naked-eye 3D system that provides an immersive and interactive viewing experience. Further researches can focus more on measurement accuracy and face landmark detection. Current system implement face localization by a standard face model, which may not be accurate enough for different users. Another possible improvementis tracker part, since assuming head movement as a complexier motion model may provide a more accurate result.

\clearpage

